\problemname{The Bus Card}
You are going to purchase a bus card.
It's a refillable card that cash can be deposited into, and then used to ride the bus until you are out of money.
You know that you're planning to travel for $K$ Swedish crowns (SEK).
Charging the card takes some time since you can only charge it with $100$, $200$ or $500$ SEK at a time.

At the moment you are in a hurry, so you want to make as few transactions as possible, but never insert more money than necessary.
If you are to travel for $800$ SEK, this means you should load it with $500$, then $200$, and then $100$ SEK.
On the other hand, if you are traveling for $850$ SEK you should load it first with $500$, and then $200$ SEK twice.
$50$ SEK will be wasted, but it's still the best alternative.

Compute the minimum number of transactions necessary.

\section*{Input}
The input consists of the integer $K$ ($1 \le K \le 10\,000$), the amount you will travel for.

\section*{Output}
Print a single integer: the number of transactions necessary.

\section*{Scoring}
Your solution will be tested on a set of test case groups.
To get the points for a group, you need to pass all the test cases in the group.

\noindent
\begin{tabular}{| l | l | p{10cm} |}
    \hline
    \textbf{Group} & \textbf{Point value} & \textbf{Constraints} \\ \hline
    $1$    & $33$        & you will never have to insert more money than the amount you travel for. \\ \hline 
    $2$    & $67$        & No additional constraints \\ \hline
\end{tabular}
